### 2021-04-15 sections/model_overview/main.tex
Apply suggestions from code review
Co-authored-by: Vince Knight <vincent.knight@gmail.com>

The problem studied is a 3-player game theoretic scenario between two queueing 
systems and a service that distributes individuals to them. 
Each player in this game has its own objectives and cares about meeting its own 
targets.
More specifically, the queueing systems' objective is captured by an upper bound
of the time that a fixed proportion of individuals need to spend in the system, 
while the distributor aims to minimise the time that its individuals 
are blocked.

@@

where \(W\) is the waiting time of all individuals, \textit{Target} is the time 
target and \(\hat{P}\) is the percentage of individuals need to be within that 
target. 
There are numerous objective functions that can be used to capture this 
behaviour. 
The first one would be to use the threshold that maximises the probability that 
the mean waiting is more than the target time, and completely ignore the 
percentage goal.

@@

Perhaps a more sophisticated objective function would be to get the proportion 
of individuals as close to the percentage aim. 
In other words, to find the threshold that minimises the difference between the 
probability and the percentage goal (or maximise its negation).

@@

Here, the purpose of \(\alpha\) is to tune the ``importance'' of each objective,
where high \(\alpha\) indicates a higher weight on the proportion of lost 
individuals and smaller \(\alpha\) a higher weight on the time blocked.

Using equations \ref{eq:obj-queueing-systems} and \ref{eq:obj-distributor}, an
imperfect information extensive form game may arise. 
An imperfect information game is defined as an extensive form game where some 
of the information about the game state is hidden for at least one of the 
players \cite{Berwanger2008}. In this study the state of the problem that is
hidden is the threshold that each player chooses to play.
In other words, each queueing system chooses to play a strategy without the 
knowing the other system's strategy.
The distributor then, fully aware of the chosen strategies are, distributes 
individuals among the two systems in order to minimise the time that its 
individuals will be blocked.

@@

Figure \ref{fig:imperfect-info-game} illustrates such a game works. The first 
queueing system \(H_A\) decides on a threshold, then the second system \(H_B\)
chooses its own threshold, without knowing the strategy of \(H_A\), and finally
the distributor makes its choice. Note here that the dotted line represents the
fact that \(H_B\) is unaware of the state of the game when making its own 
decisions. The game can thus be partitioned into a normal form game between the
two queueing systems and finding the distributor's best choice.

@@

Based on the choice of strategy of these two players the distributor will then 
make its own choice of the proportion of individuals to send to each system.

>>>>

The problem studied is a 3-player normal form game.

 The players are:

 \begin{itemize}

      \item The decision makers of two queueing 
systems;
      \item a service that distributes individuals to these two queueing systems.
 \end{itemize}

Each player in this game has its own objectives and cares about meeting its own 
targets.
More specifically, the queueing systems' objective is captured by an upper bound
of the time that a fixed proportion of individuals  spend in the system, 
while the distributor aims to minimise the time that its individuals 
are blocked.   % TODO Depending on how this is described earlier, we might need a little more here (as to what we mean by "blocked")

@@

where \(W\) is the waiting time of all individuals, \textit{Target} is the time 
target and \(\hat{P}\) is the percentage of individuals need to be within that 
target. 
There are numerous objective functions that can be used to capture this 
behaviour. 
For example one approach is to use the threshold that maximises the probability that 
the mean waiting is more than the target time, and completely ignore the 
percentage goal.

@@

A more sophisticated objective function would be to get the proportion 
of individuals as close to the percentage aim. 
In other words, to find the threshold that minimises the difference between the 
probability and the percentage goal (or maximise its negation).

@@

Here, \(\alpha\) represents the ``importance'' of each objective,
where high \(\alpha\) indicates a higher weight on the proportion of lost 
individuals and smaller \(\alpha\) a higher weight on the time blocked.

Using equations \ref{eq:obj-queueing-systems} and \ref{eq:obj-distributor}, an
imperfect information extensive form game may arise. 
An imperfect information game is defined as an extensive form game where some 
of the information about the game state is hidden for at least one of the 
players \cite{Berwanger2008}. In this study the state of the problem that is
hidden is the threshold that each of the first two players chooses to play.
In other words, each queueing system chooses to play a strategy without the 
knowing the other system's strategy.
The distributor then, fully aware of the chosen threshold strategies, distributes 
individuals among the two systems in order to minimise the time that its 
individuals will be blocked. Figure \ref{fig:imperfect-info-game} illustrates this.

@@

The first 
queueing system \(H_A\) decides on a threshold, then the second system \(H_B\)
chooses its own threshold, without knowing the strategy of \(H_A\), and finally
the distributor makes its choice. Note here that the dotted line represents the
fact that \(H_B\) is unaware of the state of the game when making its own 
decisions. The game can thus be partitioned into a normal form game between the
two queueing systems and finding the distributor's best choice.

@@

Based on the choice of strategy of these two players the distributor will then 
make their own choice of the proportion of individuals to send to each system.
